\documentclass{article}

\begin{document}
\title{SRRI Code Standards} \date{June 28 2013}
\maketitle

\begin{abstract}
  This document outlines the standards decided upon for coding the
  SRRI Datagames project. If you update this document at any time, be
  sure to change the 'date' tag to the date of your update.
\end{abstract}


\section{Variable Definitions}

\begin{itemize}
\item Variable defintions should be prefixed with either m, or k,
  depending on whether they represent a variable, or constant
  respectively.
\item The prefix character should always be lowercase. Start each word
  after that with uppercase.
\item Variables should be named according to the value that they
  represent. Look at other variables in document if you need help with
  naming.
\item Instance variables should be private.
\end{itemize}


\section{Function Definitions}

\begin{itemize}
\item The opening brace should be on the same line as the function
  name.
\item Functions are named in camel case, i.e. likeThisOneIsNamed.
\end{itemize}


\section{Commenting}

\begin{itemize}
\item Comments for a function should be written on the line above the
  function definition. If the line ends up being very long, break it
  into two lines around 70 characters.
\item In-line comments may be added within function
  definitions. Insert comments after the end of the line. If inline
  comments end up too long, select them, and press CMD-i to block them
  together.
\item There are never enough comments. Program as literately as
  possible.
\end{itemize}


\section{Packages}

\begin{itemize}
\item Packages will be named in all lowercase, and with the \_
  character representing a space. Use of the default package is
  prohibited.
\item Each game will have a 'main' package containing the .MXML and
  related source. This package will always be one word chosen based on
  the game title.
\item If you have created several classes that together serve a
  purpose, create a package for them inside of the main package.
\end{itemize}


\section{Whitespace}

\begin{itemize}
\item Leave one blank line between each method/function that you
  define. If there is a comment above a function, leave a line between
  the end of your function, and the comment.
\item Generally, leave one space character between parameters. This
  includes arguments to a function/method, as well as anywhere you
  have a comma between items in a list. i.e.
\begin{verbatim}
private var mArrayTest:Array = [1, 2, 3, 4];

private function testFunc(arg1:int, arg2:int):void{
    ...
}
\end{verbatim}
\end{itemize}


\section{Code Example}

\begin{verbatim}
package test_package{
    
    private var mTestVar:Number = 1.618;
    
    public static const kTestConst:Number = 1.618;
    
    //Here is the comment explaining what testFunc does
    private function testFunc(arg1:String, arg2:Number):void{
        ...
    }
    
    //Here is the comment explaining what testFunc does
    private function testFunc(arg1:String, arg2:Number):void{
        ... //here is an example of an inline comment
    }
}
\end{verbatim}

\end{document}
